Sweep Z - general experiment analysis.

### 2018-04-03 voltagebudget/analysis/sweep_Z_analysis.Rmd
Update Z vis Rmd

```{r, message=FALSE}
# Osc
freq <- "8"

# Zs scan
exp <- "78"
Zs <- c("0.1", "0.2", "0.3")

results <- NULL
for(Z in Zs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", freq, "_Z", Z, ".csv", sep="")
  df <- read_csv(paste(name, sep=","))

@@

# Ref (Z=0)
exp <- "77"
name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
df <- read_csv(paste(name, sep=","))
df$Zs <- rep(0, nrow(df))
results <- rbind(df, results)

# Process
results %>% 
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  mutate(V_osc = V_osc - V_osc_ref) %>% 
  mutate(silent = n_spikes_ref == 0) -> results

@@

```{r, fig.width=1.9, fig.height=1}
results %>% 
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_grid(.~Zs) +
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

>>>>

```{r, message=FALSE}
# Osc
freq <- "20"

# Zs scan
exp <- "92"
Zs <- c("0.1", "0.2", "0.3")

results <- NULL
for(Z in Zs){
  name <- paste("../data/exp", exp, "_Z", Z, ".csv", sep="")
  df <- read_csv(paste(name, sep=","))

@@

# Ref (Z=0)
exp <- "91"
name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
df <- read_csv(paste(name, sep=","))
df$Zs <- rep(0, nrow(df))
results <- rbind(df, results)

# Process
results %>% 
  filter(n_spikes_ref > 0) %>% 
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  mutate(V_osc = V_osc - V_osc_ref) %>% 
  mutate(silent = n_spikes_ref == 0) -> results

@@

```{r, fig.width=1.9, fig.height=1}
results %>% 
  filter(V_osc/V_comp <= 1) %>% 
  filter(n_spikes >0) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_grid(.~Zs) +
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.1, alpha=0.5, color="purple", linetype="dashed") +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```
